Inferring community characteristics in labelled networks

### 2021-05-27 nips/appendices.tex
SUBMIT

Recall that in 
Section~\ref{s:sfb} we used 
the Metropolis Adjusted Langevin Algorithm (MALA)
in order to 
sample from the $\theta$-chain of the block membership 
generator parameters.
At iteration $t$, the proposed sample is generated by:
%
\begin{equation}
	\theta' = \theta^{(t)} - h_t \nabla U(\theta^{(t)}) + \sqrt{2h_t} \cdot \xi.
\end{equation}
%
There are two competing objectives when choosing the step-size $h_t$. 
On the one hand, $h_t$ needs to be large so that the sampler
arrives at a high density region quickly,
while too large a step-size would lead to low acceptance rates and thus 
inefficient sampling. An effective strategy is
to use {\em simulated annealing}: allow $h_t$ to slowly decrease
with $t$, as long as $h_t>0$ for all $t$ and also:
%
\begin{equation}
	\sum_{t=1}^{\infty} h_t = \infty, \qquad \textrm{and} \qquad
	\sum_{t=1}^{\infty} h_t^2 < \infty.
	\label{eqn:h-constraints}
\end{equation}
%
Following \citet{Bayesian-SGLD}, we adopt the 
polynomially decaying step-sizes,
%
$h_t = \alpha(\beta + t)^{-\gamma}$,
%
where $\alpha>0$, $\beta>0$ and $\gamma\in(1/2,1]$ are hyper-parameters.
We make the specific choices,
%
\begin{equation}
	\alpha = \frac{250 \cdot s}{N}, \qquad \beta = 1000, \qquad \gamma = 0.8,
	\label{eqn:step-size-params}
\end{equation}
%
where $N$ is the number of data-points and $s$,
the {\em step-size scaling}, is the only free parameter.

@@

When sampling from the $b$- and $\theta$-chains described
in Section~\ref{sec:inference}, we generate
$T_b$ and $T_\theta$ samples total, respectively.
We discard an initial proportion $\kappa_\star\in(0,1)$ of the samples 
as corresponding to a ``burn-in'' period required for the distribution 
of the chain to reach a distribution close to our target,
and we also ``thin'' the remaining samples to 
obtain a less-dependent version. For $\star\in\{b,\theta\}$,
the remaining sample sets are denoted $\Tcal_\star$
in the notation of Section~\ref{s:ss},
%
\begin{equation}
	\Tcal_\star = \{T_\star \kappa_\star + i \lambda_\star :  
	0 \leq i \leq \lfloor T_\star(1 - \kappa_\star) / \lambda_\star \rfloor \},
\end{equation}
%
where $\lambda_\star$ controls the thinning. The choice of
$\kappa_\star$ can be determined by plotting the log-target (either $S(b^{(t)})$ 
or $U(\theta^{(t)})$ as a function of $t$,
and choosing $\kappa_\star$ to encompass the region where the log-target has 
roughly reached equilibrium. As we do not leverage sample independence,
$\lambda_\star$ can be chosen less rigorously; we often simply
use $\lambda_b=5$ and $\lambda_\theta = 10$.

@@

\clearpage
\section{Derivations}
\subsection{Derivation of conditional block distribution given feature matrix}
\label{appdx:b|x}

We determine the form of $p(b| X)$ by integrating
out the parameters $\theta$. From the definitions we have:
%
\begin{align*}
	p(b | X) &= \int p(b , \theta| X, \theta) d\theta = \int p(b | X, \theta) p(\theta | X) d\theta \\
	&=\int p(b | X, \theta) p(\theta) d\theta = \int \prod_{i \in [N] } \phi_{b_i}(x_i; \theta) p(\theta) d\theta \\
	&= \prod_{i \in [N]} \int \frac{\exp(w_{b_i}^T \tilde{x}_i) \prod_{j \in [B]} \Gaussian(w_j; 0, \sigma_\theta^2 I)}{\sum_{k \in [B]} \exp(w_{k}^T \tilde{x}_i)} dw_{1:B}.
\end{align*}
%
The key observation here is that 
the value of the integral is independent
of the value of $b_i \in [B]$:
The integrand has the same form regardless of $b_i$,
because the prior is the same for each $w_j$. 
Therefore, the integral is only a function of $\tilde{x}_i$ and $\sigma_\theta^2$,
which means that, as function of $b$, $p(b|X)\propto 1$. And as
$b$ takes values in $[B]^N$, we necessarily have:
%
\begin{equation}
	p(b | X) = \frac{1}{\big|[B]^N\big|}=B^{-N}.
\end{equation}

@@

Recall from~(\ref{eq:U}) in Section~\ref{s:sfb} that,
$$	\pi_\theta(\theta) \propto p(\theta | X, b) \propto p(b | X, \theta) p(\theta) \propto  \exp \left( - U(\theta) \right),
$$ 
so that $U$ can be expressed as,
$$
	U(\theta) 
= - \left( \log p(b | X, \theta) + \log p(\theta) \right) + \textrm{const}.
$$
Writing,
$y_{ij} \coloneqq \one \left\{ b_i = j \right\}$ and 
$a_{ij} \coloneqq \phi_j(x_i; \theta)$, we have,
%
\begin{equation}
	\log p(b | X, \theta) = \sum_{i \in [N]} \sum_{j \in [B]} y_{ij} \log a_{ij}  \quad \textrm{and} \quad
	\log p(\theta) = -\frac{(D+1)(B)}{2} \log 2\pi - \frac{1}{2 \sigma_\theta^2} 
\|\theta \|^2,
	\label{eqn:U-constituent-terms}
\end{equation}
%
where
$\|\theta\|^2 = \sum_{i} \theta_{i}^2 = \sum_{j=1}^{B} \|w_j\|^2$ 
is the Euclidean norm of the vector of parameters $\theta$.
Therefore, discarding constant terms, we 
obtain exactly the representation~(\ref{eqn:U-form}), as claimed.

\subsection{Derivation of {\boldmath $\;\nabla U(\theta)$}}
\label{appdx:gradu}
Here we show how the gradient 
$\nabla U(\theta)$ can be computed explicitly.
Recall the expression for $U(\theta)$ in~(\ref{eqn:U-form}).
Writing $\theta$ as
$\theta = \left[w_1^T, w_2^T \dots w_B^T  \right]^T$,
in order to compute the gradient
$\nabla U(\theta)$ we need to compute
each of its components,
$\nicefrac{\partial U}{\partial w_k}$,
$1\leq k\leq B$.
To that end, we first compute,
%
\begin{align}
	\frac{\partial a_{ij}}{\partial w_k} &= \frac
	{\tilde{x}_i \exp(w_j^T \tilde{x}_i) \delta_{jk} \cdot \sum_{r \in [B]} \exp(w_r^T \tilde{x}_i) 
		- 
		\exp(w_j^T \tilde{x}_i) \cdot \tilde{x}_i \exp(w_k^T \tilde{x}_i)}
	{\left( \sum_{r \in [B]} \exp(w_r^T \tilde{x}_i) \right)^2} \nonumber \\
	&= \tilde{x}_i \left( a_{ij} \delta_{jk} - a_{ij}a_{ik} \right), 
	\label{eq:dadw}
\end{align}
%
where $\delta_{jk} \coloneqq \one \left\{ j = k \right\}$,
and we also easily find,
%
\begin{equation}
	\frac{ \partial}{\partial w_k} \|\theta\|^2 = \frac{\partial}{\partial w_k} \left( \sum_{r \in [B]} \|w_r\|^2 \right) = 2w_k.
\label{eq:dtsdw}
\end{equation}
%
Using~(\ref{eq:dadw}) and~(\ref{eq:dtsdw}), we obtain,
\begin{align}
	\frac{\partial U}{\partial w_k} &= 
	\sum_{i=1}^{N} \sum_{j=1}^{B} y_{ij} 
	\left( -\frac{\tilde{x}_i}{a_{ij}} \left( a_{ij} \delta_{jk} - a_{ij} a_{ik} \right) \right)
	+ \frac{w_k}{\sigma_\theta^2} \nonumber \\
	&=  - \left( \sum_{i=1}^{N} \tilde{x}_i \left( y_{ik} - a_{ik} \sum_{j=1}^{B} y_{ij} \right)
	- \frac{w_k}{\sigma_\theta^2} \right) \nonumber \\
	&= - \left( \sum_{i=1}^{N} \Big\{ \tilde{x}_i (y_{ik} - a_{ik}) \Big\} - \frac{w_k}{\sigma_\theta^2} \right).
\end{align}
%
This can be computed 
efficiently through matrix operations. The only property of $y_{ij}$ 
we have used in the derivation is the constraint $\sum_{j=1}^{B} y_{ij} = 1$,
for all $i$.

@@

\begin{algorithm} % enter the algorithm environment
	\caption{Block membership sample generation} % give the algorithm a caption
	\label{alg:b-samples} % and a label for \ref{} commands later in the document
	\begin{algorithmic} % enter the algorithmic environment
		\State $b^{(0)} \gets \argmin_b S(b|A)$ \Comment{Implemented as greedy heuristic in \textit{graph-tool} library}
		\For{$t \in \{0, 1 \dots T_b - 1\}$}
		\State $b' \gets \sim q_b(b^{(t)}, b' | A)$
		\State $\log \alpha_b \gets \log \alpha_b(b^{(t)}, b' | A)$
		\State $\eta \gets \sim \textrm{Unif}(0,1)$
		\If{$\log \eta < \log \alpha_b$}
		\State $b^{(t+1)} \gets b'$
		\Else
		\State $b^{(t+1)} \gets b^{(t)}$
		\EndIf
		\EndFor

		\State \textbf{return} $\{b^{(t)}\}_{t=1}^{T_b}$

	\end{algorithmic}
\end{algorithm}

\begin{algorithm} % enter the algorithm environment
	\caption{FFBM parameter pseudo-marginal inference} % give the algorithm a caption
	\label{alg:theta-samples} % and a label for \ref{} commands later in the document
	\begin{algorithmic} % enter the algorithmic environment

		\State $\hat{Y}_{ij} \gets \frac{1}{|\Tcal_b|} \sum_{t \in \Tcal_b} \one \{ b^{(t)}_i = j\} \quad \forall i,j$
		\State $\theta^{(0)} \gets \sim \Gaussian(0, \sigma_\theta I)$

@@

		\For{$t \in \{0, 1 \dots T_\theta - 1\}$}
		\State $\xi \gets \sim \Gaussian(0, I)$
		\State $\theta' \gets \theta^{(t)} - h_t \nabla U(\theta^{(t)} | X, \hat{Y}) + \sqrt{2h_t} \cdot \xi$
		\State $\log \alpha_\theta \gets \log \alpha_\theta(\theta^{(t)}, \theta' | A, \hat{Y})$
		\State $\eta \gets \sim \textrm{Unif}(0,1)$
		\If{$\log \eta < \log \alpha_\theta$}
		\State $\theta^{(t+1)} \gets \theta'$
		\Else
		\State $\theta^{(t+1)} \gets \theta^{(t)}$
		\EndIf
		\EndFor

		\State \textbf{return} $\{\theta^{(t)}\}_{t=1}^{T_\theta}$

	\end{algorithmic}
\end{algorithm}

@@

\begin{table}[!h]
	\centering
	\caption{Compute-time for each experiment.}
	\label{tab:compute-time}
	\begin{tabular}{c|ccc|c}
		Dataset & $b$-chain & $\theta$-chain & Reduced $\theta$-chain & Overall compute time \\ \hline
		Polbooks & $\sim$1s & $\sim$4s & -- & $\sim$5s \\
		School & $\sim$10s & $\sim$10s & $\sim$10s & $\sim$30s \\
		FB Egonet & $\sim$20s & $\sim$180s & $\sim$10s & $\sim$210s
	\end{tabular}
\end{table}

>>>>

Recall that in 
Section~\ref{s:sfb} we used 
the Metropolis Adjusted Langevin Algorithm (MALA)
to 
sample from the $\theta$-chain of the block membership 
generator parameters.
At iteration $t$, the proposed sample is generated by:
%
\begin{equation}
	\theta' = \theta^{(t)} - h_t \nabla U(\theta^{(t)}) + \sqrt{2h_t} \cdot \xi.
\end{equation}
%
There are two competing objectives when choosing the step-size $h_t$. 
On the one hand, $h_t$ needs to be large so that the sampler
arrives at a high density region quickly,
while too large a step-size would lead to low acceptance rates and thus 
inefficient sampling. An effective strategy is
to use {\em simulated annealing}: allow $h_t$ to slowly decrease
with $t$, as long as $h_t>0$ for all $t$ and also:
%
\begin{equation}
	\sum_{t=1}^{\infty} h_t = \infty, \qquad \textrm{and} \qquad
	\sum_{t=1}^{\infty} h_t^2 < \infty.
	\label{eqn:h-constraints}
\end{equation}
%
Following \citet{Bayesian-SGLD}, we adopt the 
polynomially decaying step-sizes,
%
$h_t = \alpha(\beta + t)^{-\gamma}$,
%
where $\alpha>0$, $\beta>0$ and $\gamma\in(1/2,1]$ are hyper-parameters.
We make the specific choices,
%
\begin{equation}
	\alpha = \frac{250 \cdot s}{N}, \qquad \beta = 1000, \qquad \gamma = 0.8,
	\label{eqn:step-size-params}
\end{equation}
%
where $N$ is the number of data-points and $s$,
the {\em step-size scaling}, is the only free parameter.

@@

When sampling from the $b$ and $\theta$-chains described
in Section~\ref{sec:inference}, we respectively generate
$T_b$ and $T_\theta$ samples total.
We discard an initial proportion $\kappa_\star\in(0,1)$ of the samples 
as corresponding to a ``burn-in'' period required for the distribution 
of the chain to reach a distribution close to our target,
and we also ``thin'' the remaining samples to 
obtain a less-dependent version. For $\star\in\{b,\theta\}$,
the remaining sample sets are denoted $\Tcal_\star$
in the notation of Section~\ref{s:ss},
%
\begin{equation}
	\Tcal_\star = \{T_\star \kappa_\star + i \lambda_\star :  
	0 \leq i \leq \lfloor T_\star(1 - \kappa_\star) / \lambda_\star \rfloor \},
\end{equation}
%
where $\lambda_\star$ controls the thinning. The choice of
$\kappa_\star$ can be determined by plotting the log-target (either $S(b^{(t)})$ 
or $U(\theta^{(t)})$ as a function of $t$,
and choosing $\kappa_\star$ to encompass the region where the log-target has 
roughly reached equilibrium. As we do not leverage sample independence,
$\lambda_\star$ can be chosen less rigorously; we often simply
use $\lambda_b=5$ and $\lambda_\theta = 10$.

@@

\section{Derivations}
\subsection{Derivation of conditional block distribution given feature matrix}
\label{appdx:b|x}

We determine the form of $p(b| X)$ by integrating
out the parameters $\theta$. From the definitions we have:
%
\begin{align*}
	p(b | X) &= \int p(b , \theta| X, \theta) d\theta = \int p(b | X, \theta) p(\theta | X) d\theta \\
	&=\int p(b | X, \theta) p(\theta) d\theta = \int \prod_{i \in [N] } \phi_{b_i}(x_i; \theta) p(\theta) d\theta \\
	&= \prod_{i \in [N]} \int \frac{\exp(w_{b_i}^T \tilde{x}_i) \prod_{j \in [B]} \Gaussian(w_j; 0, \sigma_\theta^2 I)}{\sum_{k \in [B]} \exp(w_{k}^T \tilde{x}_i)} dw_{1:B}.
\end{align*}
%
The key observation here is that 
the value of the integral is independent
of the value of $b_i \in [B]$ as
the integrand has the same form regardless of $b_i$. This is
because the prior is the same for each $w_j$. 
Therefore, the integral is only a function of $\tilde{x}_i$ and $\sigma_\theta^2$,
which means that, as a function of $b$, $p(b|X)\propto 1$. As
$b$ takes values in $[B]^N$, we necessarily have:
%
\begin{equation}
	p(b | X) = \frac{1}{\big|[B]^N\big|}=B^{-N}.
\end{equation}

@@

Recall from~(\ref{eq:U}) in Section~\ref{s:sfb} that,
$$	\pi_\theta(\theta) \propto p(\theta | X, b) \propto p(b | X, \theta) p(\theta) \propto  \exp \left( - U(\theta) \right),
$$ 
so that $U$ can be expressed as,
$$
	U(\theta) 
= - \left( \log p(b | X, \theta) + \log p(\theta) \right) + \textrm{const}.
$$
Writing,
$y_{ij} \coloneqq \one \left\{ b_i = j \right\}$ and 
$a_{ij} \coloneqq \phi_j(x_i; \theta)$, we have that,
%
\begin{equation}
	\log p(b | X, \theta) = \sum_{i \in [N]} \sum_{j \in [B]} y_{ij} \log a_{ij}  \quad \textrm{and} \quad
	\log p(\theta) = -\frac{(D+1)(B)}{2} \log 2\pi - \frac{1}{2 \sigma_\theta^2} 
\|\theta \|^2,
	\label{eqn:U-constituent-terms}
\end{equation}
%
where
$\|\theta\|^2 = \sum_{i} \theta_{i}^2 = \sum_{j \in [B]} \|w_j\|^2$ 
is the Euclidean norm of the vector of parameters $\theta$.
Therefore, discarding constant terms, we 
obtain exactly the representation~(\ref{eqn:U-form}), as claimed.

\subsection{Derivation of {\boldmath $\;\nabla U(\theta)$}}
\label{appdx:gradu}
Here we show how the gradient 
$\nabla U(\theta)$ can be computed explicitly.
Recall the expression for $U(\theta)$ in~(\ref{eqn:U-form}).
Writing $\theta$ as
$\theta = \left[w_1^T, w_2^T \dots w_B^T  \right]^T$,
in order to compute the gradient
$\nabla U(\theta)$ we need to compute
each of its components,
$\nicefrac{\partial U}{\partial w_k}$,
$1\leq k\leq B$.
To that end, we first compute,
%
\begin{align}
	\frac{\partial a_{ij}}{\partial w_k} &= \frac
	{\tilde{x}_i \exp(w_j^T \tilde{x}_i) \delta_{jk} \cdot \sum_{r \in [B]} \exp(w_r^T \tilde{x}_i) 
		- 
		\exp(w_j^T \tilde{x}_i) \cdot \tilde{x}_i \exp(w_k^T \tilde{x}_i)}
	{\left( \sum_{r \in [B]} \exp(w_r^T \tilde{x}_i) \right)^2} \nonumber \\
	&= \tilde{x}_i \left( a_{ij} \delta_{jk} - a_{ij}a_{ik} \right), 
	\label{eq:dadw}
\end{align}
%
where $\delta_{jk} \coloneqq \one \left\{ j = k \right\}$,
and we also easily find,
%
\begin{equation}
	\frac{ \partial}{\partial w_k} \|\theta\|^2 = \frac{\partial}{\partial w_k} \left( \sum_{r \in [B]} \|w_r\|^2 \right) = 2w_k.
\label{eq:dtsdw}
\end{equation}
%
Using~(\ref{eq:dadw}) and~(\ref{eq:dtsdw}), we obtain,
\begin{align}
	\frac{\partial U}{\partial w_k} &= 
	\sum_{i \in [N]} \sum_{j \in [B]} y_{ij} 
	\left( -\frac{\tilde{x}_i}{a_{ij}} \left( a_{ij} \delta_{jk} - a_{ij} a_{ik} \right) \right)
	+ \frac{w_k}{\sigma_\theta^2} \nonumber \\
	&=  - \left( \sum_{i \in [N]} \tilde{x}_i \left( y_{ik} - a_{ik} \sum_{j \in [B]} y_{ij} \right)
	- \frac{w_k}{\sigma_\theta^2} \right) \nonumber \\
	&= - \left( \sum_{i \in [N]} \Big\{ \tilde{x}_i (y_{ik} - a_{ik}) \Big\} - \frac{w_k}{\sigma_\theta^2} \right).
\end{align}
%
This can be computed 
efficiently through matrix operations. The only property of $y_{ij}$ 
we have used in the derivation is the constraint $\sum_{j \in [B]} y_{ij} = 1$,
for all $i$.

@@

\begin{algorithm} % enter the algorithm environment
	\caption{Block membership sample generation} % give the algorithm a caption
	\label{alg:b-samples} % and a label for \ref{} commands later in the document
	\begin{algorithmic} % enter the algorithmic environment
		\Procedure{SampleBlockMemberships}{$A, T_b$}
		\State $b^{(0)} \gets \argmin_b S(b|A)$ \Comment{Implemented as greedy heuristic in \textit{graph-tool} library}
		\For{$t \in \{0, 1 \dots T_b - 1\}$}
		\State $b' \gets \sim q_b(b^{(t)}, b' | A)$
		\State $\log \alpha_b \gets \log \alpha_b(b^{(t)}, b' | A)$
		\State $\eta \gets \sim \textrm{Unif}(0,1)$
		\If{$\log \eta < \log \alpha_b$}
		\State $b^{(t+1)} \gets b'$
		\Else
		\State $b^{(t+1)} \gets b^{(t)}$
		\EndIf
		\EndFor

		\State \textbf{return} $\{b^{(t)}\}_{t=1}^{T_b}$
		\EndProcedure
	\end{algorithmic}
\end{algorithm}

\begin{algorithm} % enter the algorithm environment
	\caption{FFBM parameter pseudo-marginal inference} % give the algorithm a caption
	\label{alg:theta-samples} % and a label for \ref{} commands later in the document
	\begin{algorithmic} % enter the algorithmic environment
		\Procedure{SampleFeatureWeights}{$X, \{b^{(t)}\}, \Tcal_b, \sigma_\theta, s$}
		\State $\hat{Y}_{ij} \gets \frac{1}{|\Tcal_b|} \sum_{t \in \Tcal_b} \one \{ b^{(t)}_i = j\} \quad \forall i,j$
		\State $\theta^{(0)} \gets \sim \Gaussian(0, \sigma_\theta I)$

@@

		\For{$t \in \{0, 1 \dots T_\theta - 1\}$}
		\State $\xi \gets \sim \Gaussian(0, I)$
		\State $h_t \gets \frac{s}{N} \cdot 250(1000 + t)^{-0.8}$
		\State $g_t \gets \nabla U(\theta^{(t)}| X, \hat{Y})$
		\item[]
		\State $\theta' \gets \theta^{(t)} - h_t \cdot g_t + \sqrt{2h_t} \cdot \xi$
		\State $\log \alpha_\theta \gets \log \alpha_\theta(\theta^{(t)}, \theta' | A, \hat{Y})$
		\State $\eta \gets \sim \textrm{Unif}(0,1)$
		\If{$\log \eta < \log \alpha_\theta$}
		\State $\theta^{(t+1)} \gets \theta'$
		\Else
		\State $\theta^{(t+1)} \gets \theta^{(t)}$
		\EndIf
		\EndFor

		\State \textbf{return} $\{\theta^{(t)}\}_{t=1}^{T_\theta}$
		\EndProcedure
	\end{algorithmic}
\end{algorithm}

\begin{algorithm} % enter the algorithm environment
	\caption{Dimensionality reduction} % give the algorithm a caption
	\label{alg:retained-set} % and a label for \ref{} commands later in the document
	\begin{algorithmic} % enter the algorithmic environment
		\Procedure{ReduceDimension}{$\{W^{(t)}\}, \Tcal_\theta, k, D'$}

		\State $(B, D) \gets W^{(0)}$.shape
		\State $\hat{\mu}_{ij} \gets \frac{1}{|\Tcal_\theta|} \sum_{t \in \Tcal_\theta} W_{ij}^{(t)} \quad \forall i \in [B], j \in [D]$
		\State $\hat{\sigma}_{ij} \gets \frac{1}{|\Tcal_\theta|} \sum_{t \in \Tcal_\theta} \left( W_{ij}^{(t)} - \hat{\mu}_{ij} \right)^2 \quad \forall i \in [B], j \in [D]$

		\For{$d \in [D]$}
		\For{$i \in [B]$}
		\State $l_i \gets \hat{\mu}_{id} - k \cdot \hat{\sigma}_{id}$
		\State $u_i \gets \hat{\mu}_{id} + k \cdot \hat{\sigma}_{id}$
		\If{$l_i \leq 0$ and $u_i \geq 0$}
		\State $l_i, u_i \gets 0$
		\EndIf
		\EndFor
		\State $c_d \gets \max_i \min\left(|l_i|, |u_i| \right)$
		\EndFor

		\State indexArray $\gets$ indexSort($c$, descending=True)[$0:D'$]
		\State $d^* \gets$ indexArray[-1]
		\State $\Dcal' \gets $ Set(indexArray)
		\State $c^* \gets c_{d^*}$
		\State \textbf{return} $\Dcal', c^*$
		\EndProcedure
	\end{algorithmic}
\end{algorithm}

@@

\begin{table}[!h]
	\centering
	\caption{Compute-time for each experiment}
	\label{tab:compute-time}
	\begin{tabular}{c|ccc|c}
		Dataset & $b$-chain & $\theta$-chain & Reduced $\theta$-chain & Overall compute time \\ \hline
		Polbooks & $\sim$1s & $\sim$10s & -- & $\sim$11s \\
		School & $\sim$1s & $\sim$7s & $\sim$7s & $\sim$15s \\
		FB Egonet & $\sim$2s & $\sim$50s & $\sim$8s & $\sim$60s
	\end{tabular}
\end{table}

### 2021-05-27 nips/conclusion.tex
SUBMIT

Using this new model,
we go on to describe an efficient inference algorithm to sample 
the parameters $\theta$ of the feature-to-block generator. 
This takes the form of two concurrent Markov chains,
used to sample the block memberships $b$ and block generator 
parameters $\theta$. These chains can either be executed
in parallel or 
the empirical mean of the $b$-samples can be used
as the input to the $\theta$-chain. The latter option
reduces the variance in our evaluation of the target distribution 
and thus shortens burn-in.

The overall method is shown to be effective at extracting and describing 
the most natural communities in a labelled network. Nevertheless, the approach 
can only currently explain the structure at the macro-scale. We cannot 
explain structure within each block. Future work will benefit from extending 
the FFBM to be hierarchical in nature. That way, the structure of the network 
can be explained at all several scales of interest. So long as data 
collection techniques remain ethical and care is taken to respect 
personal privacy, such empowered decision-making can only help humankind.

>>>>

Using this new model,
we go on to describe an efficient inference algorithm to sample 
the parameters $\theta$ of the feature-to-block generator. 
This takes the form of a two-level Markov chain,
used to sample the block memberships $b$ and block generator 
parameters $\theta$. These chains can either be executed
in parallel or 
the empirical mean of the $b$-samples can be used
as the input to the $\theta$-chain. The latter option
reduces the variance in our evaluation of the target distribution 
and thus shortens burn-in.

The overall method is shown to be effective at extracting and describing 
the most natural communities in a labelled network. Nevertheless, the approach 
can only currently explain the structure at the macro-scale. We cannot 
explain structure within each block. Future work will benefit from extending 
the FFBM to be hierarchical in nature. That way, the structure of the network 
can be explained at all length-scales of interest. So long as data 
collection techniques remain ethical and care is taken to respect 
personal privacy, such empowered decision-making can only help humankind.
